---
title: "Plots for Dr. Chapman"
output: pdf_document
---

### Goal

In this document, I will plot the original fitted univariate effects across tissues, and the estimated 'shrunken effects' using the method `mashr` from (Urbut et al, 2018)[https://www.biorxiv.org/content/early/2016/12/24/096552].

The goal here is to estimate genetic ffects across tissues on gene expression for eQTL of genes known to be involved in kidney pathogenesis.

```{r,include=FALSE}
library('knitr')

library('rmeta')
```

You can find the *ENSG* name for each gene in the ```genes=which(rownames)==ensg``` command.

```{r exampleuk3,echo=F}


source("~/Dropbox/gtexresults_matrixashold/Scripts/normfuncs.R")

z.stat=read.table("~/Dropbox/gtexresults_matrixashold/Data/maxz.txt")
b.stat=read.table("~/Dropbox/gtexresults_matrixashold/Data/maxbetahats.txt")

standard.error=b.stat/z.stat





covmat=readRDS("~/Dropbox/gtexresults_matrixashold/Data_vhat/covmatwithvhat.rds")
posterior.means=read.table("~/Dropbox/gtexresults_matrixashold/Data_vhat/withvhatposterior.means.txt")[,-1]
lfsr=read.table("~/Dropbox/gtexresults_matrixashold/Data_vhat/withvhatlfsr.txt")[,-1]
mar.var=read.table("~/Dropbox/gtexresults_matrixashold/Data_vhat/withvhatmarginal.var.txt")[,-1]
colnames(lfsr)=colnames(mar.var)=colnames(posterior.means)=colnames(z.stat)

posterior.betas=standard.error*posterior.means
pm.beta.norm=het.norm(posterior.betas)


missing.tissues=c(7,8,19,20,24,25,31,34,37)
color.gtex=read.table("~/Dropbox/gtexresults_matrixashold/Data/GTExColors.txt",sep = '\t', comment.char = '')[-missing.tissues,]

uk3labels=read.table("~/Dropbox/gtexresults_matrixashold/Data/uk3rowindices.txt")[,1]

col = as.character(color.gtex[uk3labels,2])


barplot(seq(1:44),col=col,names=colnames(lfsr[,uk3labels]),las=2,main="Legend",cex.names=0.5)


missing.tissues=c(7,8,19,20,24,25,31,34,37)
uk3labels=read.table("~/Dropbox/gtexresults_matrixashold/Data/uk3rowindices.txt")[,1]

newfunc.2=function(j){
gtex.colors=read.table('~/Dropbox/gtexresults_matrixashold/Data/GTExColors.txt', sep = '\t', comment.char = '')[-missing.tissues,2]
gtex.colors=gtex.colors[uk3labels]




pm.beta.norm=pm.beta.norm[,uk3labels]##shufflecolumns
z.shuffle=z.stat[,uk3labels]
b.shuffle=b.stat[,uk3labels]
post.var=mar.var[uk3labels]
post.bshuffle=posterior.betas[,uk3labels]
sem.shuffle=standard.error[,uk3labels]
lfsr=lfsr[,uk3labels]
title=strsplit(rownames(z.stat)[j], "[.]")[[1]][1]




x=as.numeric(post.bshuffle[j,])

par(mfrow=c(1,1))
metaplot(as.numeric(b.shuffle[j,]),as.numeric(sem.shuffle[j,]),xlab = "",ylab="",colors=meta.colors(box=as.character(gtex.colors)),xlim=c(-1,1))
title(title)

par(mfrow=c(1,1))
sd=as.numeric(sem.shuffle[j,])*sqrt(as.numeric(post.var[j,]))##to transform to posterior sd of beta
metaplot(x,sd,xlab = "",ylab="",colors=meta.colors(box=as.character(gtex.colors)),xlim=c(-1,1))
title(title)
}
````

Here we plot PKD2:
```{r cars}

PKD2=which(rownames(z.stat)=="ENSG00000118762.3_4_88908136_C_A_b37")
newfunc.2(PKD2)
```

Here we plot PKD1:
```{r}
PKD1=which(rownames(z.stat)=="ENSG00000008710.13_16_2195198_T_C_b37")

newfunc.2(PKD1)

source("https://bioconductor.org/biocLite.R")
biocLite("biomaRt")
```

No data for these guys:
```{r,eval=F}
PKD1L1
ENSG00000158683

PKD1L2
ENSG00000166473 

PKD2L1
ENSG00000107593


PKD2L2
ENSG00000078795


TSC1
ENSG00000165699 
```

```{r}
TSC2=which(rownames(z.stat)=="ENSG00000103197.12_16_2138218_A_C_b37")

newfunc.2(TSC2)

VHL=which(rownames(z.stat)=="ENSG00000134086.7_3_10177653_C_T_b37")
newfunc.2(VHL)

GANAB=which(rownames(z.stat)=="ENSG00000089597.12_11_62413662_C_T_b37")
newfunc.2(GANAB)



BBS1=which(rownames(z.stat)=="ENSG00000174483.15_11_65435127_T_C_b37")
newfunc.2(BBS1)

BBS2=which(rownames(z.stat)=="ENSG00000125124.7_16_56506126_C_A_b37")
newfunc.2(BBS2)

BBS7=which(rownames(z.stat)=="ENSG00000138686.5_4_122746285_TC_T_b37")
newfunc.2(BBS7)


BBS12=which(rownames(z.stat)=="ENSG00000181004.5_4_124533552_T_C_b37")
newfunc.2(BBS12)
```


